### 2012-09-17 doc/prelim/document/chapters/introduction/introduction.tex
cleaning up chapter structure in prelim

In order to achieve this high fidelity, state-of-the-art computing
facilities must be leveraged in a way that is both efficient and
considerate of hardware-related issues. As scientific computing moves
towards exascale facilities with machines of $O(1,000,000)$ cores
already coming online, new algorithms to solve these complex problems
must be developed to leverage this new hardware. Issues such as
resiliency to node failure and scaling to large numbers of cores will
be pertinent to robust algorithms aimed at this new
hardware. Considering these issues, this thesis proposes the
development of a massively parallel stochastic method for linear
problems and a novel stochastic method to advance solution techniques
for nonlinear problems with the aim of improving the modeling of
coupled physics systems for nuclear reactor analysis.

@@

>>>>

In order to achieve this high fidelity, state-of-the-art computing
facilities must be leveraged in a way that is both efficient and
considerate of hardware-related issues. As scientific computing moves
towards exascale facilities with machines of $O(1,000,000)$ cores
already coming online, new algorithms to solve these complex problems
must be developed to leverage this new hardware. Issues such as
resiliency to node failure and scaling to large numbers of cores will
be pertinent to robust algorithms aimed at this new
hardware. Considering these issues, this thesis proposes the
development of a massively parallel stochastic method for linear
problems and a novel stochastic method to advance solution techniques
for nonlinear problems.

@@

\section{The Multiphysics System}
\label{sec:multiphysics_system}

\section{Research Outline}
\label{sec:research_outline}

### 2012-09-17 doc/prelim/document/chapters/linear_problem/linear_problem.tex
cleaning up chapter structure in prelim

>>>>

\section{Parallel Methods for Solving Sparse Linear Systems}
\label{sec:parallel_krylov_methods}
Modern parallel implementations of Krylov methods on distributed
memory architectures rely heavily on capabilities provided by general
linear algebra frameworks. This arises from the fact that Krylov
methods require only a handful of operations in their
implementation. Per Saad's text \citep{saad_2003}, these operations
are preconditioning, matrix-vector multiplications, vector updates,
and dot products. For the last three items, linear algebra libraries
such as PETSc \citep{petsc_2012} and Trilinos \citep{trilinos_2005}
provide efficient parallel implementations for these
operations. Depending on the type of preconditioning used, efficient
parallel implementations may also be available for those
operations. In all cases, a series of scatter/gather operations are
required such that global communication operations must
occur. Therefore, the performance of such operations is bound to the
implementation. However, asymptotically perfomance should be the same
across all implementations.

\section{Parallelization of the MCSA Algorithm}
\label{section:parallel_mcsa}
For the prelim, I suspect that I will not have a parallel MCSA
algorithm up and running as I will be focusing on generating the code
base needed to build the physics operators and tools for linear and
nonlinear systems analysis. Therefore, here we should focus on
motivating a parallel scheme for this work. We should start by first
looking at current parallel methods for solving linear systems using
the conventional techniques from the previous chapter. It must be
clearly pointed out that for the new hardware coming online, these
methods (or at least their current implementations) will be lacking in
scalability and the potential for resiliency, and therefore a parallel
MCSA is attractive, even if it ultimately does not show performance
gains from a wall time perspective.

Once we have done this, MSOD will need to be defined. The literature
is actually quite lacking here even for reactor physics problems as
this is really bleeding edge. Therefore, I should strive here to more
rigorously define this methodology in terms of solving general linear
systems. Furthermore, we should discuss the aspects of being able to
vary the overlap such that we can generate a spectrum between complete
domain decomposition and complete domain replication. Finally, the
beginnings of the algorithm should be sketched out.

\subsection{Multiple-Set Overlapping-Domain Decomposition}
\label{subsec:msod}

### 2012-09-17 doc/prelim/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding references
updates to prelim, projection methods section is complete
cleaning up chapter structure in prelim

\section{Formulation of the Nonlinear System}
\label{sec:nonlinear_system}

@@

\subsection{General Newton Methods}
\label{subsec:newton_methods}

@@

\section{Preconditioning the Nonlinear System}
\label{sec:nonlinear_preconditioning}

\section{Time Integration}
\label{sec:time_integration}

\section{Applications to Model Problems}
\label{sec:nonlinear_applications}

>>>>

\section{Preliminaries}
\label{sec:nonlinear_preliminaries}

@@

\subsection{Inexact Newton Methods}
\label{subsec:newton_methods}

@@

\section{The FANM Method}
\label{sec:fanm}
In this section we will devise the FANM method. Based on the
background in the previous section, we first need to motivate the
development of this work by pointing out some of the issues with
conventional methods. This includes JFNK coarseness and either
prohibitively large Krylov subspaces or a loss of orthogonality
information in the subspace due to restarts. We can than point out
some of the attractive qualities of the FANM method. Much of this will
rely on advanced concepts including automatic differentiation and
on-the-fly residual and Jacobian generation from nonlinear function
evaluations. In addition, we will want to show that the Newton method
will converge using MCSA as the linear solver. I suspect I will have
some preliminary results for a serial implementation here as I already
have a serial MCSA implemented. Finally, we will want to design the
model problems that we will test FANM with. These should be problems
that have already been worked up in the literature with benchmark-type
solutions.

\subsection{Automatic Differentiation}
\label{sec:automatic_differentiation}

\subsection{Residual and Jacobian Generation}
\label{sec:fanm_generation}

\subsection{Jacobian Storage vs. Subspace Storage and Restarts}
\label{sec:fanm_storage}
